Parsing Tweets into Universal Dependencies

### 2018-01-27 naacl2018_rebuttal.txt

We thank all the reviewers for your comments.

To the first reviewer:

- "There appear to be two conventions in UD for handling cases like 'gonna' … I would like to see some argumentation for why the authors adapt the first convention."

If we don't consider the normalization, the second convention can be recovered from the first one using the 'SpaceAfter' feature in the last column of our annotation. And it's arguable that normalization on social media data is essential according to Esenstain (2013). Thus, we preserve the original tweet content as much as possible while respecting the UD guideline. What's more, adopting the first convention makes it easier for us to train our parser from the combination of our annotation and the UD_English treebank since they are of the same convention.

- "I would like to see some discussion of why normalization/lemmatization is ignored and why the authors think it does not hurt POS tagging and parsing performance."

As mentioned before, we basically follow the spirit of Essenstain (2013) in treating normalization on social media content. Since he pointed out normalization for social media data is vaguely defined and often impossible without changing the meaning, we don’t include normalization in our annotation. We believe it's an open question and needs more careful study. We also believe that a clean form of the social media content benefits downstream POS and parsing, but reaching this level of cleanness is non-trivial for social media content. So we didn't consider them in our paper.

To the second reviewer:

- "yet do not offer annotation of the more fine­-grained schema from Gimpel et al. (2011)"

We use the second POS column to retain the Gimpel's POS annotation on the overlapped part.

- "I wish authors submitted a sample of 10 tweets as supplementary material"

We will release our data and the reader of this paper can refer to our release for sanity check and future development.

- "authors did not specifically state efforts of tweet anonymization (non­celebrity handles, urls) but the examples exhibit them."

We will make the anonymization effort more clear in future revision.

- "(7) Table 5 and related discussion: is this the greedy or CRF setup?"

It's the CRF setup. We will make it more clear in future revision.

- "how exactly are the F1/accuracy scores computed? Per token? Token boundary?"

It's computed on token.

- "While training the POS tagger on GloVe embeddings, was there a problem with OOV words?"

The compared neural POS taggers from Ma and Hovy (2016) uses a character-CNN as an additional word representation, which can mitigate the OOV problems.

To the third reviewer:

- "In relation to "training with exploration", it would have been relevant to cite the original papers on dynamic oracles (Goldberg and Nivre, 2012, 2013) as well as the paper by Kiperwasser and Goldberg (2016)"

We would cite the dynamic oracle work in our future revision.

- "It is worth pointing out that UD does not use the tag set of Petrov et al. (2012) but a revised and extended version of it (with 17 tags instead of 12)."

We meant the 17 tags set and we will revise our wording in future revision.

### 2018-01-28 naacl2018_rebuttal.txt

We would cite the dynamic oracle work in our future revision.

- "It is worth pointing out that UD does not use the tag set of Petrov et al. (2012) but a revised and extended version of it (with 17 tags instead of 12)."

We meant the 17 tags set and we will revise our wording in future revision.

- "The claim that "UD tokenisation treats each syntactic word as a token" is confused"

[To be completed by Yi]

- "Using the relation 'discourse' for 'non-syntactic tokens' is highly dubious. it seems better to use the generic relation 'dep'."

The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specified guidelines for this. Our choice of 'discourse' was inspired by the observation that emoticon is annotated as 'discourse' in UD_English. However, non-syntactic tokens can be easily recovered from our annotation and changing it to other relation in the future development is not difficult.

- "how is sentence segmentation performed? Is every tweet regarded as exactly one sentence?"

We treat every tweet as exactly one sentence in both our annotation and parser but allow more than one root.

- "Are you using a static oracle in all experiments except the one that explicitly mentions exploration? Is it fair to use a dynamic oracle only for the parser with distillation? "

Yes. We use static oracle in our experiment. It's a good suggestion and we would add dynamic oracle baseline in our future revision. Our distillation without exploration can be treated as a fair comparison with the static oracle baseline and our distillation with exploration further improve the performance.

- "There seems to be an apostrophe missing in 'its is tokenised as it and s when is is a copula'."

'its' is an example of the informal nature of tweets that author omit the apostrophe.

### 2018-01-29 naacl2018_rebuttal.txt

We thank all the reviewers for your comments.

To the first reviewer:

- "There appear to be two conventions in UD for handling cases like 'gonna' … I would like to see some argumentation for why the authors adapt the first convention."

If we don't consider the normalization,/*YI did not know what you mean by 'if we don't consider normalization'*/ the second convention can be recovered from the first one using the 'SpaceAfter' feature in the last column of our annotation./*YI maybe show a line as example?*/ And it's arguable that normalization on social media data is essential according to Esenstain (2013) /*YI (could be problematic if do normalization)*/. Thus, we preserve the original tweet content as much as possible while respecting the UD guideline. What's more, adopting the first convention makes it easier for us to train our parser from the combination of our annotation and the UD_English treebank since they are of the same convention.
/*YI another motivation is UD_English consists of web domain text, we think it is reasonable/compatible to follow UD's convention dealing with the web domain texts.*/

@@

- "I would like to see some discussion of why normalization/lemmatization is ignored and why the authors think it does not hurt POS tagging and parsing performance."

As mentioned before, we basically follow the spirit of Essenstain (2013) in treating normalization on social media content. Since he pointed out normalization for social media data is vaguely defined and often impossible without changing the meaning, we don’t include normalization in our annotation. We believe it's an open question and needs more careful study./*YI maybe also follow UD_English normalization convention? need to check*/ We also believe that a clean form of the social media content benefits downstream POS and parsing, but reaching this level of cleanness is non-trivial for social media content./*YI for both annotation and models*/ So we didn't consider them in our paper.

@@

To the second reviewer:

- "yet do not offer annotation of the more fine­-grained schema from Gimpel et al. (2011)"

We use the second POS column to retain the Gimpel's POS annotation on the overlapped part. /*YI Did we? or say we will include POS tags in the second col of POS. More compatability issue. Gimpel's schema is great, but difficult to generalize across domain/language within UD framework. For example, we also use UD_English as training data, which would be very difficult to incorporate with if we adopt Gimpel's POS*/

@@

- "I wish authors submitted a sample of 10 tweets as supplementary material"

We will release our data and the reader of this paper can refer to our release for sanity check and future development.

- "Telling from 3 examples, 2 of which are artificial and one whose POS tagging isn't shown, is not enough for a sanity check of annotation and scheme worth."

/*YI we will add the POS to the example in the paper.*/

@@

- "authors did not specifically state efforts of tweet anonymization (non­celebrity handles, urls) but the examples exhibit them."

We will make the anonymization effort clearer in future revision./*YI Ask Noah*/

@@

It's the CRF setup. We will make it clearer in future revision.

- "how exactly are the F1/accuracy scores computed? Per token? Token boundary?"

It's computed on token.

- "interannotator agreement: is this figure computed over all annotators? More details are needed."

We have multiple annotators, these are two major(representative) and plausible annotations.

@@

- "It is worth pointing out that UD does not use the tag set of Petrov et al. (2012) but a revised and extended version of it (with 17 tags instead of 12)."

We meant the 17 tags set and we will revise our wording in future revision.

- "The claim that "UD tokenisation treats each syntactic word as a token" is confused"

We do need to revise the statements as we are wrong about the subject of the sentence (UD) and not rigorous enough. 
This is actually our tokenization principle, that we treat each syntactic word as a token. We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna) and treat them as new tokens. It is the same as UD conventions. However, we use goeswith relation to resolve multi-token words instead of combining them back as one option suggested by UD.

- "Tagging a title with an internal syntactic structure (like "Fix you") as a proper noun is a clear violation of UD guidelines."

(From UD_English train example)
20	author	author	NOUN	NN	Number=Sing	8	conj	8:conj	_
21	of	of	ADP	IN	_	24	case	24:case	_
22	"	"	PUNCT	``	_	24	punct	24:punct	SpaceAfter=No
23	Sacred	Sacred	PROPN	NNP	Number=Sing	24	compound	24:compound	_
24	Space	Space	PROPN	NNP	Number=Sing	20	nmod	20:nmod	_
25	and	and	CCONJ	CC	_	27	cc	27:cc	_
26	Holy	Holy	PROPN	NNP	Number=Sing	27	compound	27:compound	_
27	War	War	PROPN	NNP	Number=Sing	24	conj	24:conj	SpaceAfter=No

18	the	the	DET	DT	Definite=Def|PronType=Art	19	det	19:det	_
19	book	book	NOUN	NN	Number=Sing	16	obl	16:obl	_
20	Disposable	Disposable	PROPN	NNP	Number=Sing	21	compound	21:compound	_
21	Patriot	Patriot	PROPN	NNP	Number=Sing	19	appos	19:appos	SpaceAfter=No

2	the	the	DET	DT	Definite=Def|PronType=Art	3	det	3:det	_
3	Beatles	Beatles	PROPN	NNPS	Number=Plur	5	nmod:poss	5:nmod:poss	SpaceAfter=No
4	'	'	PART	POS	_	3	case	3:case	_
5	song	song	NOUN	NN	Number=Sing	11	obl	11:obl	_
6	"	"	PUNCT	``	_	7	punct	7:punct	SpaceAfter=No
7	Get	get	VERB	VB	VerbForm=Inf	5	appos	5:appos	_
8	Back	back	ADV	RB	_	7	advmod	7:advmod	SpaceAfter=No
9	"	"	PUNCT	''	_	7	punct	7:punct	_

From most UD_English examples about titles, we are misled by the proper noun with adjective combinations where UD annotates the adjective as PROPN. However, after double checking POS PROPN, we realized that it violated the UD annotation. We will correct it in both our paper and the data repo.

@@

- "Using the relation 'discourse' for 'non-syntactic tokens' is highly dubious. it seems better to use the generic relation 'dep'."

The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specified guidelines for this./*For example, we did write to UD_English asking them the explanation for URLs as list relation, but still did not get answer.*/ Our choice of 'discourse' was inspired by the observation that emoticon is annotated as 'discourse' in UD_English./*YI And tokens like username and hashtags, as non-syntactic tokens, do look like emoticons providing extra information to tweets.*/ However, non-syntactic tokens can be easily recovered from our annotation and changing it to other relation in the future development is not difficult./*Our attempt to categorization of the relations to the non-syntactic tokens are just the first attemps and we believe it could be further refined with more and more researcher involved in.*/

@@

- "how is sentence segmentation performed? Is every tweet regarded as exactly one sentence?"

We treat every tweet as exactly one sentence in both our annotation and parser but allow more than one root.
/*YI Isn't is one tweet have many sentences with their own roots, and all roots connects to a single dummy root??*/

### 2018-01-30 naacl2018_rebuttal.txt

We thank all the reviewers for your comments.

To the first reviewer:

- "There appear to be two conventions in UD for handling cases like 'gonna' ... The latter seems more powerful and introduce linguistically motivated/normalized tokens. I would like to see some argumentation for why the authors adapt the first convention."

Without the normalization process, the second convention can be converted from the first one using the 'SpaceAfter' feature in the last column of our annotation (see the following CoNLL-X formatted snippet for example). And it's arguable that normalization on social media data is essential according to Eisenstein (2013). Thus, we preserve the original tweet content as much as possible while respecting the UD guideline. What's more, adopting the first convention makes it easier for us to train our parser from the combination of our annotation and the UD_English treebank (We use UD_English thanks to its relatively large scale and web domain) since they are of the same convention.
...
5 gon _ VERB _ _ 3 parataxis _ SpaceAfter=No
6 na _ PART _ _ 7 mark _
...

@@

- "I would like to see some discussion of why normalization/lemmatization is ignored and why the authors think it does not hurt POS tagging and parsing performance."

As mentioned before, we basically follow the spirit of Eisenstein (2013) in treating normalization on social media content. Since he pointed out normalization for social media data is vaguely defined and often impossible without changing the meaning, we don't include normalization in our annotation. We believe it's an open question and needs more careful study. We also believe that a clean form of the social media content benefits downstream POS and parsing, but reaching this level of cleanness is non-trivial for social media content for both the annotation and model. So we didn't consider them in our paper.

@@

To the second reviewer:

- "yet do not offer annotation of the more fine­-grained schema from Gimpel et al. (2011)"

We would use the second POS column to retain the Gimpel's POS annotation on the overlapped part.

@@

- "I wish authors submitted a sample of 10 tweets as supplementary material"

We will release our data and the reader of this paper can refer to our release for sanity check and future development.

- "Telling from 3 examples, 2 of which are artificial and one whose POS tagging isn't shown, is not enough for a sanity check of annotation and scheme worth."

We will add the POS to the example in the paper.

@@

- "authors did not specifically state efforts of tweet anonymization (non­celebrity handles, urls) but the examples exhibit them."

We will make the anonymization effort clearer in future revision.

@@

It's the CRF setup. We will make it clearer in future revision.

- "how exactly are the F1/accuracy scores computed? Per token? Token boundary?"

It's computed on token.

- "interannotator agreement: is this figure computed over all annotators? More details are needed."

We have multiple annotators, these are two major (representative) and plausible annotations.

@@

- "It is worth pointing out that UD does not use the tag set of Petrov et al. (2012) but a revised and extended version of it (with 17 tags instead of 12)."

We meant the 17 tags set and we will revise our wording in future revision.

- "The claim that "UD tokenisation treats each syntactic word as a token" is confused"

We do need to revise the statements as we are wrong about the subject of the sentence (UD) and not rigorous enough.
This is actually our tokenization principle, that we treat each syntactic word as a token. We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna) and treat them as new tokens. It is the same as UD conventions. However, we use goeswith relation to resolve multi-token words instead of combining them back as one option suggested by UD.

- "Tagging a title with an internal syntactic structure (like "Fix you") as a proper noun is a clear violation of UD guidelines."

During our annotation, some of our annotators was referring to the UD_English for cases that they are not sure and the UD_English presents some cases that violate the guidelines for title (see http://bionlp-www.utu.fi/dep_search/query?search=Sacred&db=UD_English-v2&case_sensitive=True&hits_per_page=50). This kind of disagreements was resolved in the final version. We will clarify this in the draft in our future revision.

@@

- "Using the relation 'discourse' for 'non-syntactic tokens' is highly dubious. it seems better to use the generic relation 'dep'."

The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specified guidelines for this. Our choice of 'discourse' was inspired by the observation that emoticon is annotated as 'discourse' in UD_English. However, non-syntactic tokens can be easily recovered from our annotation and changing it to other relation in the future development is not difficult. Our attempt to categorization of the relations to the non-syntactic tokens are just the first attempts and we believe it could be further refined with more and more researcher involved in.

@@

- "how is sentence segmentation performed? Is every tweet regarded as exactly one sentence?"

We segment sentences in one tweet with punctuation and retweet symbol (RT). We will clarify this in the future revision.

@@

- "Are you using a static oracle in all experiments except the one that explicitly mentions exploration? Is it fair to use a dynamic oracle only for the parser with distillation? "

Yes. We use static oracle in our experiment. It's a good suggestion and we would add dynamic oracle baseline in our future revision. Our distillation without exploration can be treated as a fair comparison with the static oracle baseline and our distillation with exploration further improve the performance.

- "There seems to be an apostrophe missing in 'its is tokenised as it and s when is is a copula'."

'its' is an example of the informal nature of tweets that the author omits the apostrophe.

### 2018-01-30 naacl2018_rebuttal.txt

As mentioned before, we basically follow the spirit of Eisenstein (2013) in treating normalization on social media content. Since he pointed out normalization for social media data is vaguely defined and often impossible without changing the meaning, we don't include normalization in our annotation. We believe it's an open question and needs more careful study. We also believe that a clean form of the social media content benefits downstream POS and parsing, but reaching this level of cleanness is non-trivial for social media content for both the annotation and model. So we didn't consider them in our paper.

To the second reviewer:

- "yet do not offer annotation of the more fine­-grained schema from Gimpel et al. (2011)"

We will use the second POS column to retain the Gimpel's POS annotation on the overlapped part.

@@

- "how exactly are the F1/accuracy scores computed? Per token? Token boundary?"

It's computed on token.

- "interannotator agreement: is this figure computed over all annotators? More details are needed."

We have multiple annotators, these are two major, representative and plausible annotations.

@@

The compared neural POS taggers from Ma and Hovy (2016) uses a character-CNN as an additional word representation, which can mitigate the OOV problems.

To the third reviewer:

- "In relation to "training with exploration", it would have been relevant to cite the original papers on dynamic oracles (Goldberg and Nivre, 2012, 2013) as well as the paper by Kiperwasser and Goldberg (2016)"

We will cite the dynamic oracle work in our future revision.

@@

- "It is worth pointing out that UD does not use the tag set of Petrov et al. (2012) but a revised and extended version of it (with 17 tags instead of 12)."

We meant the 17 tags set and we will revise our wording in future revision.

- "The claim that "UD tokenisation treats each syntactic word as a token" is confused"

We do need to revise the statements as we are wrong about the subject of the sentence (UD) and not rigorous enough.
It is actually our tokenization principle, that we treat each syntactic word as a token. We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna to gon na) and treat them as new tokens. It is the same as UD conventions. However, we use "goeswith" relation to resolve multi-token words instead of combining them back as one option suggested by UD.

@@

- "Tagging a title with an internal syntactic structure (like "Fix you") as a proper noun is a clear violation of UD guidelines."

During our annotation, some of our annotators was referring to the UD_English for cases of titles they are not sure about, some of which are exceptions, where nouns and proper nouns with adjectives are all annotated as PROPN for POS tag, (see http://bionlp-www.utu.fi/dep_search/query?search=Sacred&db=UD_English-v2&case_sensitive=True&hits_per_page=50). This kind of disagreements was resolved in the final version. We will clarify this in the draft in our future revision.

@@

- "Using the relation 'discourse' for 'non-syntactic tokens' is highly dubious. it seems better to use the generic relation 'dep'."

The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specified guidelines for this. Our choice of 'discourse' was inspired by the observation that emoticons and interjections are annotated as 'discourse' in UD_English. However, non-syntactic tokens can be easily recovered from our annotation and changing their relations to others in the future development is not difficult. Our decision to categorize non-syntactic tokens into the 'discourse' label is just the first attempt and we believe it could be further refined with more and more researchers involved in.

### 2018-01-31 naacl2018_rebuttal.txt

We thank all the reviewers for your comments.

To the first reviewer:

- "There appear to be two conventions in UD for handling cases like 'gonna' ... The latter seems more powerful and introduce linguistically motivated/normalized tokens. I would like to see some argumentation for why the authors adapt the first convention."

Without the normalization process, the second convention can be converted from the first one using the 'SpaceAfter' feature in the last column of our annotation (see the following CoNLL-X formatted snippet for example).

...
5 gon _ VERB _ _ 3 parataxis _ SpaceAfter=No
6 na _ PART _ _ 7 mark _
...

And it's arguable that normalization of social media data is essential according to Eisenstein (2013). Thus, we preserve the original tweet content as much as possible while respecting the UD guidelines. What's more, adopting the first convention makes it easier for us to train our parser from the combination of our annotation and the UD_English treebank, since they follow the same conventions. (We use UD_English thanks to its relatively large scale and web domain.)

@@

- "I would like to see some discussion of why normalization/lemmatization is ignored and why the authors think it does not hurt POS tagging and parsing performance."

As mentioned before, we basically follow the spirit of Eisenstein (2013) in treating normalization of social media content. Since he pointed out that normalization for social media data is vaguely defined and often impossible without changing the meaning, we don't include normalization in our annotation. Of course, we believe it's an open question and needs more careful study. We concede that a clean, canoncial form for social media content would benefit downstream POS and parsing, but those transformations are non-trivial for both the annotation and model.  In this paper, we prioritized compatibility with UD, but we expect that future work will explore integration of normalization into such pipelines.

@@

- "yet do not offer annotation of the more fine­-grained schema from Gimpel et al. (2011)"

We will use the second POS column to retain the Gimpel's POS annotation on the overlapped part.

- "I wish authors submitted a sample of 10 tweets as supplementary material"

We will release our data and use the extra space to provide more examples of the annotations.

@@

- "Telling from 3 examples, 2 of which are artificial and one whose POS tagging isn't shown, is not enough for a sanity check of annotation and scheme worth."

We will add the POS to the examples in the paper.

- "authors did not specifically state efforts of tweet anonymization (non­celebrity handles, urls) but the examples exhibit them."

We will make the anonymization effort clear in the next version.

@@

- "how exactly are the F1/accuracy scores computed? Per token? Token boundary?"

It's computed on token.

- "interannotator agreement: is this figure computed over all annotators? More details are needed."

We have multiple annotators, these are two representative and plausible annotations.

@@

- "While training the POS tagger on GloVe embeddings, was there a problem with OOV words?"

The compared neural POS tagger from Ma and Hovy (2016) uses a character-CNN as an additional word representation, which can mitigate the OOV problems.

@@

- "In relation to "training with exploration", it would have been relevant to cite the original papers on dynamic oracles (Goldberg and Nivre, 2012, 2013) as well as the paper by Kiperwasser and Goldberg (2016)"

We will cite the dynamic oracle work in the next version.

- "It is worth pointing out that UD does not use the tag set of Petrov et al. (2012) but a revised and extended version of it (with 17 tags instead of 12)."

We meant the 17-tag tagset and we will revise our wording in the next version.

@@

- "The claim that "UD tokenisation treats each syntactic word as a token" is confused"

You are correct; this statement needs to be revised.  What we should have said is that *our* approach to tokenization treats each syntactic word as a token.  We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna to gon na) and treat them as new tokens. It is the same as UD conventions. However, we use the "goeswith" relation to resolve multi-token words instead of combining them back [!!!this is ambiguous -- what is the one option suggested by UD?  using goeswith or combining them back?] as one option suggested by UD.

@@

- "Tagging a title with an internal syntactic structure (like "Fix you") as a proper noun is a clear violation of UD guidelines."

During our annotation, some of our annotators referred to the UD_English for cases of titles they are not sure about, some of which are exceptions, where nouns and proper nouns with adjectives are all annotated as PROPN for POS tag, (see http://bionlp-www.utu.fi/dep_search/query?search=Sacred&db=UD_English-v2&case_sensitive=True&hits_per_page=50). This kind of disagreement was resolved in the final version. We will clarify this in the next version.

@@

- "Using the relation 'discourse' for 'non-syntactic tokens' is highly dubious. it seems better to use the generic relation 'dep'."

The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specific guidelines for this. Our choice of 'discourse' was inspired by the observation that emoticons and interjections are annotated as 'discourse' in UD_English. However, non-syntactic tokens can be easily recovered from our annotation and changing their relations to others in the future development is not difficult. Our decision to categorize non-syntactic tokens into the 'discourse' label might be revisited as more researchers become involved in the interface between UD and social media text.

@@

- "how is sentence segmentation performed? Is every tweet regarded as exactly one sentence?"

We segment sentences in one tweet with punctuation [!!!this is too vague] and the retweet symbol (RT). We will clarify this in the future revision.

@@

- "Are you using a static oracle in all experiments except the one that explicitly mentions exploration? Is it fair to use a dynamic oracle only for the parser with distillation? "

Yes. We use static oracle in our experiment. It's a good suggestion and we will add dynamic oracle baseline in the next version. Our distillation without exploration can be treated as a fair comparison to the static oracle baseline and our distillation with exploration further improves the performance.

@@

- "There seems to be an apostrophe missing in 'its is tokenised as it and s when is is a copula'."

In carefully edited text, there should be an apostrophe as 'its' is a contraction of 'it' and 'is'.  However, here, 'its' is an example of the informal nature of tweets -- the author omitted the apostrophe.

### 2018-02-01 naacl2018_rebuttal.txt

- "Tagging a title with an internal syntactic structure (like "Fix you") as a proper noun is a clear violation of UD guidelines."

During our annotation, some of our annotators referred to the UD_English for cases of titles they are not sure about, some of which are exceptions, where nouns and proper nouns with adjectives are all annotated as PROPN for POS tag, (see http://bionlp-www.utu.fi/dep_search/query?search=Sacred&db=UD_English-v2&case_sensitive=True&hits_per_page=50). This kind of disagreement was resolved in the final version. We will clarify this in the next version.

- "Using the relation 'discourse' for 'non-syntactic tokens' is highly dubious. it seems better to use the generic relation 'dep'."

The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specific guidelines for this. Our choice of 'discourse' was inspired by the observation that emoticons and interjections are annotated as 'discourse' in UD_English (see http://bionlp-www.utu.fi/dep_search/query?search=%22%3A%29%22&db=UD_English-v2&case_sensitive=True&hits_per_page=50). However, non-syntactic tokens can be easily recovered from our annotation and changing their relations to others in the future development is not difficult. Our decision to categorize non-syntactic tokens into the 'discourse' label might be revisited as more researchers become involved in the interface between UD and social media text.

@@

- "how is sentence segmentation performed? Is every tweet regarded as exactly one sentence?"

We segment sentences in one tweet with period, exclamation mark, ellipsis mark, and the retweet symbol (RT). We will clarify this in the next revision.

### 2018-03-04 paper.tex
copyedits: capitalize Universal Dependencies

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets that affect tokenization,
part-of-speech tagging, and labeled dependencies. Using the extended guidelines, we create
a new tweet treebank ({\sc Tweebank v2}) that is four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreements between our annotators
and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Nonetheless, using the new treebank,
we build a pipeline system to parse raw tweets into UD. To overcome the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 transition-based parsers into a single one. Our
parser achieves an improvement of 2.6 in LAS over the un-ensembled baseline 
and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
\end{abstract}

\section{Introduction}
NLP for social media messages is challenging, because domain
adaptation is required, and also because creating annotated datasets
(e.g., treebanks)
for training and evaluation is hard. 
Pioneering work by \citet{AAAIW113912} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank
\citep[PTB;][]{Marcus93buildinga}, enabling conversion to Stanford dependencies.
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} were introduced to enable
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptable to different genres \cite{wang-EtAl:2017:Long6} 
and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we introduce a new tweet treebank of 55,607 tokens that follows the UD
guidelines, but also contends with social media-specific challenges that were not
covered by UD guidelines. Our annotation includes 
tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
We characterize the disagreements among our annotators and find that
consistent annotation is still challenging to deliver even with
the extended guidelines.

@@

Based on these annotations, we nonetheless designed a pipeline to parse 
raw tweets into universal dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
with character-based word representations
\cite{ballesteros-dyer-smith:2015:EMNLP}, which we refer to as our
``baseline'' parser.
To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we 
distill a 20-parser ensemble into a single greedy  parser 
\cite{DBLP:journals/corr/HintonVD15}.
We show further  that learning directly from the exploration of the ensemble parser
is more beneficial than learning from the gold standard ``oracle''
transition sequence. Experimental results show that an improvement of more
than 2.6 points in LAS over the
baseline parser can be achieved with our distillation method.  It outperforms
other state-of-the-art parsers in both accuracy and speed.

The contributions of this paper include:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and create a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and labeled universal dependencies.
We also characterize the difficulties of creating such annotation.

\item We introduce and evaluate a pipeline system to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}).  Experimental results show
that it performs better than a pipeline of the state-of-the-art alternatives.

@@

We present a pipeline system to parse tweets into universal
dependencies.  We evaluate each component individually, and the system
as a whole.

@@

\section{Conclusion}
We study the problem of parsing tweets into universal dependencies.
We adapt the UD guidelines to cover 
special constructions in tweets and create
the {\sc Tweebank v2}, which has 55,607 tokens. We characterize the disagreements
among our annotators and argue that inherent ambiguity in this genre
makes
consistent annotation a challenge.  Using this new treebank,
we build a pipeline system to parse tweets into UD. We also 
propose a new method to distill an ensemble of 20 greedy parsers into a single one
to overcome annotation noise without sacrificing efficiency.
Our parser achieves an improvement of 2.6  in LAS over a strong baseline
and outperforms other state-of-the-art parsers in both accuracy and speed.

>>>>

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
Universal Dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets that affect tokenization,
part-of-speech tagging, and labeled dependencies. Using the extended guidelines, we create
a new tweet treebank ({\sc Tweebank v2}) that is four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreements between our annotators
and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Nonetheless, using the new treebank,
we build a pipeline system to parse raw tweets into UD. To overcome 
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 transition-based parsers into a single one. Our
parser achieves an improvement of 2.6 in LAS over the un-ensembled baseline 
and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
\end{abstract}

\section{Introduction}
NLP for social media messages is challenging, because domain
adaptation is required, and also because creating annotated datasets
(e.g., treebanks)
for training and evaluation is hard. 
Pioneering work by \citet{AAAIW113912} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank
\citep[PTB;][]{Marcus93buildinga}, enabling conversion to Stanford Dependencies.
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal Dependencies \citep[UD]{NIVRE16.348} were introduced to enable
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptable to different genres \cite{wang-EtAl:2017:Long6} 
and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we introduce a new tweet treebank of 55,607 tokens that follows the UD
guidelines, but also contends with social media-specific challenges that were not
covered by UD guidelines. Our annotation includes 
tokenization, part-of-speech (POS) tags, and (labeled) Universal Dependencies.
We characterize the disagreements among our annotators and find that
consistent annotation is still challenging to deliver even with
the extended guidelines.

@@

Based on these annotations, we nonetheless designed a pipeline to parse 
raw tweets into Universal Dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
with character-based word representations
\cite{ballesteros-dyer-smith:2015:EMNLP}, which we refer to as our
``baseline'' parser.
To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we 
distill a 20-parser ensemble into a single greedy  parser 
\cite{DBLP:journals/corr/HintonVD15}.
We show further  that learning directly from the exploration of the ensemble parser
is more beneficial than learning from the gold standard ``oracle''
transition sequence. Experimental results show that an improvement of more
than 2.6 points in LAS over the
baseline parser can be achieved with our distillation method.  It outperforms
other state-of-the-art parsers in both accuracy and speed.

The contributions of this paper include:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and create a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and labeled Universal Dependencies.
We also characterize the difficulties of creating such annotation.

\item We introduce and evaluate a pipeline system to parse the raw tweet text into
Universal Dependencies (\S\ref{sec:parsing}).  Experimental results show
that it performs better than a pipeline of the state-of-the-art alternatives.

@@

We present a pipeline system to parse tweets into Universal
Dependencies.  We evaluate each component individually, and the system
as a whole.

@@

\section{Conclusion}
We study the problem of parsing tweets into Universal Dependencies.
We adapt the UD guidelines to cover 
special constructions in tweets and create
the {\sc Tweebank v2}, which has 55,607 tokens. We characterize the disagreements
among our annotators and argue that inherent ambiguity in this genre
makes
consistent annotation a challenge.  Using this new treebank,
we build a pipeline system to parse tweets into UD. We also 
propose a new method to distill an ensemble of 20 greedy parsers into a single one
to overcome annotation noise without sacrificing efficiency.
Our parser achieves an improvement of 2.6  in LAS over a strong baseline
and outperforms other state-of-the-art parsers in both accuracy and speed.
